Integrated approach to modeling to krill population dynamics in Wester Antarctic Peninsula: spatial and ecosystem considerations

### 2025-03-19 index.Rmd
adding test 2

```{r message=FALSE, warning=FALSE, echo=TRUE}
dir01 <- here("s01") # agreggate data (no spatial diferences)
dir1<-here("s1") # Data strata flishery
dir2<-here("s2") # Same 9 with areas (SubStrata) as fleet. Dif size comoposition and dif CPUE and dif survey length and biomass data by strata
dir3<-here("s3") # without S-R
dir4<-here("s4") # 
dir5<-here("s5") # 
dir6<-here("s6") # 
dir7<-here("s7") # 2 set parametres EMM-2024/23 (Mardones)
dir8<-here("s8") # s1 platoons
dir9<-here("s9") # s1 w/ blocks
dirtest<-here("test")
Figs <- here("Figs")# S
```

@@

```{r message=F, include=FALSE}
#stest
base.modeltest <- SS_output(dir=dirtest,
                        covar=T,
                        forecast=T)
```

Just some time series plots

```{r}
SSplotTimeseries(base.modeltest,
                 subplot = 7)
SSplotTimeseries(base.modeltest,
                 subplot = 9)
```
and fits

>>>>

```{r message=FALSE, warning=FALSE, echo=TRUE}
dir01 <- here("s01") # agreggate data (no spatial diferences)
dir1<-here("s1") # Data strata flishery
dir2<-here("s2") # Same 9 with areas (SubStrata) as fleet. Dif size comoposition and dif CPUE and dif survey length and biomass data by strata
dir3<-here("s3") # without S-R
dir4<-here("s4") # 
dir5<-here("s5") # 
dir6<-here("s6") # 
dir7<-here("s7") # 2 set parametres EMM-2024/23 (Mardones)
dir8<-here("s8") # s1 platoons
dir9<-here("s9") # s1 w/ blocks
dirtest<-here("test") # con todo
dirtest2 <- here("test2") # sin predador ni ambiental
Figs <- here("Figs")# S
```

@@

```{r message=F, include=FALSE}
#stest
r4ss::run(
  dir = dirtest,
  exe = "ss_osx",
  skipfinished = FALSE, # TRUE will skip running if Report.sso present
  show_in_console = TRUE # change to true to watch the output go past
)
base.modeltest <- SS_output(dir=dirtest,
                        covar=T,
                        forecast=T)
```

```{r}
SSplotTimeseries(base.modeltest,
                 subplot = 1)
SSplotTimeseries(base.modeltest,
                 subplot = 9)
SSplotTimeseries(base.modeltest,
                 subplot = 7)
```
and fits
